---
title: Prediction of Petrophysics Properties using Machine Learning and Hieararchical
  Multi-task Linear Models
author: "Marcelo Ramalho Albuquerque"
date: "8/16/2020"
theme: "Madrid"
output: 
  beamer_presentation:
    slide_level: 2
    toc: false
    theme: "Hannover"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

# Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

# New Level

```{r echo = TRUE}
summary(cars)
```

## Slix

```{r presure}
plot(pressure)
```

# Conclusion

- One
- Two
